Classical Planning Algorithms ¡ on the Atari Video Games

### 2014-11-18 icaps15-paper/paper.tex
changed title

 \begin{document}
% The file aaai.sty is the style file for AAAI Press
% proceedings, working notes, and technical reports.
%
\pdfinfo{
/Title (Classical Planning Algorithms on the Atari Video Games: Preliminary Results)
/Author ( )}
% (Nir Lipovetzky, Miquel Ramirez, Hector Geffner)}

@@

\title{Classical Planning Algorithms ¡ on the Atari Video Games: Preliminary Results}

>>>>

 \begin{document}
% The file aaai.sty is the style file for AAAI Press
% proceedings, working notes, and technical reports.
%
\pdfinfo{
/Title (Classical Planning Algorithms on the Atari Video Games)
/Author ( )}
% (Nir Lipovetzky, Miquel Ramirez, Hector Geffner)}

@@

\title{Classical Planning Algorithms ¡ on the Atari Video Games}
